The \project{unRAVE} catalog

### 2016-09-08 article/unrave.tex
Update numbers with v0.95

\newcommand{\Nspectra}{520,782}
\newcommand{\Nstars}{457,589}
\newcommand{\Nstarsqc}{434,470}

@@

We have presented the largest collection of stellar abundances for stars in the 
first \gaia\ data release.  In total more than X.XX million abundances are
available, with effective temperature $\teff$, surface gravity $\logg$ and 
metallicity available for XXXXXX stars.  Despite the caveats and limitations 
discussed here, our validation experiments and comparisons with high-resolution
spectroscopic studies suggests that our results have sufficient accuracy and
precision to be useful for exoplanet host stars studies 
\citep[c.f.,][]{Valenti_Fischer_2005}, investigations of the Milky Way disk 
\citep[c.f.,][]{Reddy_2003,Reddy_2006,Bensby_2014}, and a multitude of 
chemo-dynamic studies.  When combined with positions and 3D velocities from \gaia,
we are optimistic that the \unrave\ catalog will help advance understanding 
of the Milky Way's formation and evolution.

>>>>

\newcommand{\Nspectra}{520,782}
\newcommand{\Nstars}{457,589}
\newcommand{\Nstarsqc}{447,207} % v0.95 finite values
\newcommand{\Nabundances}{1,692,825} %v0.95 finite values

@@

We have presented the largest collection of stellar abundances for stars in the 
first \gaia\ data release.  In total more than 1.69 million abundances are
available, with effective temperature $\teff$, surface gravity $\logg$ and 
metallicity available for \Nstarsqc\ stars.  Despite the caveats and limitations 
discussed here, our validation experiments and comparisons with high-resolution
spectroscopic studies suggests that our results have sufficient accuracy and
precision to be useful for exoplanet host stars studies 
\citep[c.f.,][]{Valenti_Fischer_2005}, investigations of the Milky Way disk 
\citep[c.f.,][]{Reddy_2003,Reddy_2006,Bensby_2014}, and a multitude of 
chemo-dynamic studies.  When combined with positions and 3D velocities from \gaia,
we are optimistic that the \unrave\ catalog will help advance understanding 
of the Milky Way's formation and evolution.
